---
title: "NewTarGz"
author: "Christine Iyer"
date: "July 15, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
library(rvest)
library(ggplot2)
```

```{r}
#untar("instacart.tar.gz")
```

###Most popular groceries from "shareranks"

```{r}
groceryURL <- read_html("http://shareranks.com/15836,Most-Common-Foods-Purchased-at-a-Grocery-Store")
popularGroceries <- groceryURL %>% html_nodes(".info_name") %>% html_text()  %>% 
  gsub('[\r\n\t]', '', .)
class(popularGroceries)

```


###Splurge items from epicurious

```{r}
splurgeURL <- read_html("http://www.epicurious.com/expert-advice/best-grocery-store-splurges-article")
splurgeGroceries <- splurgeURL %>% html_nodes(".article-body h4") %>% html_text()
splurgeGroceries
```

###Recyclable

```{r}
recycleURL <- read_html("http://www.motherjones.com/environment/2015/12/these-15-grocery-store-items-are-not-recyclable/")
recycleNotPackaging <- recycleURL %>% html_nodes("strong") %>% html_text()
recycleNotPackaging <- recycleNotPackaging[-c(2,6,11,15,17)]
recycleNotPackaging
```


```{r}

## or, if you just want to extract the target file:

X <- read.csv("order_products__prior.csv", header = T)

c <- read.csv("orders.csv")

Products <- read.csv("products.csv", header = T)

aa <- read.csv("aisles.csv", header = T)

train <- read.csv("order_products__train.csv", header = T)

```


```{r}
head(X)
dim(X)
```

```{r}
head(c)
dim(c)
```

```{r}
head(Products)
```

```{r}
dim(aa)
head(aa)
```

```{r}
head(train)
```
In 2015 Instacart had 206,209 customers place 3,421,083 orders  

```{r}
#m is c with the NA omitted. The NA is their first order. So there are actually no NA values. This can be deduced from the summary. 
m <- c %>% na.omit()
dim(m)
ggplot(c,aes(x = factor(days_since_prior_order))) + geom_bar()
byCustomerOrder <- m %>% group_by(user_id) %>% summarise(numberOrders = n())
summary(byCustomerOrder)
dim(c)
sum(is.na(c))
head(c, 25)
summary(c)
summary(m)

```


Want to make an interactive dataset where a customer's activity can be isolated from the others and it will show all of their orders. 


for(i in unique(UniqueData$State)){
  
  
  newDS <- UniqueData %>% filter(State == i)
  
  print(head(newDS))
  hist(newDS$Number.of.Prescriptions, main = paste(i, "'s Rx Frequency"))
  identify(newDS$Number.of.Prescriptions)
  
}

```{r}
for(i in unique(m$user_id)){
  newDSm <- m %>% filter(user_id == i)
  identity(newDSm$days_since_prior_order)
  
  
}
```


###Number of times each product is entered in the dataset

There are 32,434,489 entries in this dataset. There are 49,667 items that get reordered. 



```{r}
XX <- X %>% group_by(product_id) %>% summarise(countEntries = n()) %>% arrange(desc(countEntries))
mean(XX$countEntries)
head(XX)
dim(XX)
49667/32434489
```


###Number of times product was reordered. 

```{r}
XXX <- X %>% group_by(product_id) %>% summarise(countReordered = sum(reordered)) %>% arrange(countReordered)
head(XXX)
dim(XXX)
```

###Percent of reorders per item

First join the precious 2 tables to put the number of entries and the number of times an entry was reordered side by side. 

```{r}
XXXX <- inner_join(XX, XXX)
head(XXXX)
dim(XXXX)
```

Which products never got reordered?
There were 4,372 items that were never reordered. 

```{r}
neverReordered <- XXX %>% filter(countReordered == 0)
dim(neverReordered)
head(neverReordered)
```


```{r}
XXXXX <- XXXX %>% mutate(PercentReordered = countReordered/countEntries) %>% arrange(desc(PercentReordered))
head(XXXXX)
dim(XXXXX)
```

Distribution of reorders

```{r}
head(XXXXX)
boxplot(XXXXX$PercentReordered, ylab = "Percent of items reordered", main = "Spread of Reorders")

hist(XXXXX$PercentReordered, xlab = "Percentage of items that are reordered", ylab = "Frequency of reorders", main = "Frequency Distribution of Items Reordered")
```


Which products were reordered over 80% of the time?

```{r}
XXXXXX <- XXXXX %>% filter(PercentReordered >= 0.8)
dim(XXXXXX)
head(XXXXXX)
```

###What percent of products were reordered over 80 percent of the time?

```{r}
round(dim(XXXXXX)/dim(XXXXX), digits = 3)
```
Product Names

```{r}
Products <- read.csv("products.csv", header = T)
head(Products)
dim(Products)
```

###What are the products that were reordered over 80% of the time?


```{r}
XXXXXXX <- inner_join(Products, XXXXXX)
kable(head(XXXXXXX %>% arrange(desc(countReordered))))
head(XXXXXXX)
```

###A list of the most popular grocery items

```{r}
library(stringr)
mostPopularGroceries <- c("BANANA",
"BOTTLE",
"DEPOSIT",
"CUCUMBER",
"CREAM CHEESE",
"PEPPER",
"BUTTER",
"CARROTS",
"POTATO",
"AVOCADOS"
) 
mostPopularGroceries <-  str_to_title(mostPopularGroceries)
class(mostPopularGroceries)

RandomGroceries <- c("Pasta", "Chocolate", "Milk", "Almonds", "Nuts")
class(RandomGroceries)
RandomGroceries <- paste(RandomGroceries, collapse=" | ")
RandomGroceries
```

```{r}
XXXXXXXX <- XXXXXXX %>% filter(product_name %in% mostPopularGroceries)
XXXXXXXX

XXXXXXXX <- XXXXXXX %>% filter(grepl("Chocolate | Pasta | Milk | Almonds | Nuts | Bananas", product_name))
XXXXXXXX
XXXXXXX %>% filter(product_name %in% RandomGroceries)
XXXXXXX %>% filter(product_name %in% mostPopularGroceries)

Milk <- XXXXXXX %>% filter(grepl("Milk", product_name))
Chocolate <- XXXXXXX %>% filter(grepl("Chocolate", product_name))
Milk
Chocolate
```

###Aisles of the most reordered items. 
There are 134 different aisles. 

```{r}
#aisles aa
aa <- read.csv("aisles.csv", header = T)
dim(aa)
#there are 623 items in aisle 17
aa %>% filter(aisle_id == 17)
dim(Products %>% filter(aisle_id == 17))
head(Products%>% filter(aisle_id == 17))
#to check which aisles are busiest
w <- inner_join(Products, XXXXXXX)
r <- inner_join(w,aa)
head(r)
r %>% group_by(aisle_id, aisle) %>% summarise(sumofReorders = sum(countReordered)) %>% arrange(desc(sumofReorders))

```

```{r}
train <- read.csv("order_products__train.csv", header = T)
head(train %>% group_by(order_id) %>% summarise(numberItems = n()) %>% arrange(desc(numberItems)), 25)
dim(train %>% group_by(order_id) %>% summarise(numberItems = n()) %>% arrange(desc(numberItems)))

NumberItems <- train %>% group_by(order_id) %>% summarise(numberItems = n()) %>% arrange(desc(numberItems))
head(NumberItems)
dim(NumberItems)
```

###Days_since_prior_order. Load Data

```{r}

head(c)
summary(c)
sum(is.na(c))
ggplot(c, aes(x=days_since_prior_order)) + geom_density()
ProductsDays <- inner_join(c, train)
ProductsDays <- inner_join(ProductsDays, Products)
ProductsDays <- inner_join(ProductsDays, aa)
ProductsDays <- inner_join(ProductsDays, X)
dim(ProductsDays)
head(ProductsDays)
```
###Who orders?

```{r}
whoOrders <- c %>% group_by(user_id) %>% summarise(NumberOrders = n()) %>% arrange(desc(NumberOrders)) %>% filter(NumberOrders > 90 & NumberOrders < 100)
head(whoOrders)
```


```{r}
mostOrders <- c %>% group_by(user_id) %>% summarise(NumberOrders = n()) %>% arrange(desc(NumberOrders))
head(mostOrders)

dim(mostOrders)
ggplot(mostOrders, aes(x = NumberOrders))+ geom_bar()
ggplot(mostOrders, aes(x=NumberOrders)) + geom_density()
```


```{r}
hist(mostOrders$NumberOrders, main = "Reorder Frequency", xlab = "Number of Reorders", ylab = "Frequency of Reorders")

head(r)
head(XXXXX)
v <- inner_join(Products, XXXXX)
v <-  inner_join(v, aa)
head(v)
dim(v)
range(v$countReordered)
```


```{r, fig.height=25, fig.width=10}
ggplot(r, aes(x = PercentReordered, group = aisle, fill = aisle)) + geom_histogram(bins = 6)
head(r)
```


How often does each customer order

```{r}
howOften <- c %>% group_by(user_id) %>% summarise(days_since_prior_orderMean = mean(days_since_prior_order)) %>% arrange(desc(days_since_prior_orderMean)) 
```

```{r}

head(howOften)
# %>% filter(NumberOrders > 90 & NumberOrders < 100)
dim(whoOrders)
head(c)
head(whoOrders, 25)


```



###Aisles of items that were never reordered
The 4,372 that were never reordered

```{r}
head(neverReordered)
dim(neverReordered)
head(Products)
aislesNeverReordered <- inner_join(neverReordered, Products )
aislesNeverReordered <- inner_join(aislesNeverReordered, aa)
head(aislesNeverReordered)
```


###the items that are never reordered are spread over 131 aisles

```{r}
aislesZero <- aislesNeverReordered %>% select(product_id, product_name, aisle_id, aisle)
head(aislesZero)
aislesZero %>% group_by(aisle) %>% summarise(numberItemsintheAisle = n()) %>% arrange(desc(numberItemsintheAisle))
names(aislesZero)
dim(aislesZero)
aislesZero %>% filter(aisle == "grains rice dried goods")


```

```{r}
departments <- read.csv("departments.csv", header = T)
head(departments)

head(Products)
```

Departments and Products

```{r}
DandP <- inner_join(Products, departments)
head(DandP)
dim(DandP)
```
Mean perecent of items reordered per department

```{r}
DPV <- inner_join(DandP,v)
head(DPV)
dim(DPV)
kable(DPV %>% group_by(department) %>% summarise(numberItemsperDept = n(), meanPctReorders = round(mean(PercentReordered), digits = 3), meanNumberReorders = round(mean(countReordered), digits = 0)) %>% arrange(desc(meanNumberReorders)))
```

Busiest days of the week

```{r}

```


What items are ordered on what days

```{r}
dowVector <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
d <- read.csv("orders.csv")
kable(head(d))
e <- d
e$order_dow <- factor(e$order_dow, labels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"),
            ordered = TRUE)
kable(head(e))
str(e)
head(d %>% mutate(Day = (ifelse(order_dow == 0, "Sunday", ifelse(order_dow ==1, "Monday", ifelse(order_dow == 2, "Tuesday", ifelse(order_dow == 3, "Wednesday", ifelse(order_dow == 4, "Thursday", ifelse(order_dow == 5, "Friday", "Saturday")))))))))
range(d$order_hour_of_day)
hist(d$order_hour_of_day, main = "Most orders are between 10-4")
hist(d$order_dow, xaxt = "n", xlab = "", freq = F)



h = hist(d$order_dow)
h$density = h$counts/sum(h$counts)
plot(h,freq=FALSE, ylim = c(0, 0.20), las = 2, xaxt = "n", xlab = "", lwd = 2, lend="square")
axis(side = 1,at=seq(0,6, 1),labels = dowVector, las = 2)

```

```{r}
head(c)
daysSincePrior <- hist(c$days_since_prior_order)
daysSincePrior$density = daysSincePrior$counts/sum(daysSincePrior$counts)
plot(daysSincePrior,freq=FALSE, ylim = c(0, 0.12), las = 2, xaxt = "n",  lwd = 2, lend="square", xlab = "Days Since Prior Order", main = "Frequency of Days Between Previous Order ")
axis(side = 1, las = 2)
```

